### 2020-09-30 README.Rmd
trying out a different image
updated figure and contents in repo

# LIME Research <img align="right" height="200" src="./figures/lime.png">

@@

**code**

This folder is a place for storing code that is used throughout the project:

- `app.R`: code for the Shiny app for visualizing the LIME explanations associated with the bullet land comparisons
- `helper_functions.R`: R script with functions that I use in the journals and will probably end up using in the papers as well

**figures**

This folder contains static images:

- `lime.png`: fun picture of a lime to use in the readme
- `python-ridge1`, `python-ridge2`, and `python-ridge3`: screen shots of the python LIME package showing the use of a ridge regression as the explainer

**journals**

@@

- `00-objectives_and_ideas`: background of the research project, goals of the project, concerns with LIME, and ideas to try
- `01-hamby_data_and_models`: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
- `02-understanding_lime`: explanation of LIME procedure
- `03-applying_lime`: applications of LIME to the models fit to the Hamby data
- `04-assessing_lime`: visual diagnostics for assessing the lime explanations
- `05-iris_comparison`: applying LIME to a random forest fit to the iris data
- `06-literature_review`: notes on papers relating to LIME
- `07-computation_issues`: documentation of some of the computation issues I ran into during the project
- `08-logistic_regression`: examples of applying LIME to explain logistic regression models
- `09-refitting-rtrees`: examples where I retrain the rtrees model with the "current" version of the training data and compare the results

@@

- `.gitattributes`: attributes relating to git
- `.gitignore`: files to ignore
- `notes from Heike.pdf`: scans of notes written by Heike for this project
- `README`: document containing to do list and contents of this repository

>>>>

# LIME Research <img align="right" height="200" src="https://i.pinimg.com/originals/de/18/33/de18338e3313edd97d8156d987244e74.jpg">

@@

[**code**](code/)

Place for storing R code used in the research journals:

- [app.R](code/app.R): code for the Shiny app for visualizing the LIME explanations associated with the bullet land comparisons
- [helper_functions.R](code/helper_functions.R): R script with functions that I use in the journals

[**figures**](figures)

Contains static images:

- [laugel-lime-concept.png](figures/laugel-lime-concept.png) and [laugel-locality-metric](figures/laugel-locality-metric.png): figures from the Laugel et al. (2018) paper
- [python-ridge1](figures/python-ridge1.png), [python-ridge2](figures/python-ridge2.png), and [python-ridge3](figures/python-ridge3.png): screen shots of the python LIME package showing the use of a ridge regression as the explainer

[**journals**](journals)

@@

- [00-objectives_and_ideas](journals/00-objectives_and_ideas): background of the research project, goals of the project, concerns with LIME, and ideas to try
- [01-hamby_data_and_models](journals/01-hamby_data_and_models)***: information on the Hamby data, cleaning of the training and testing data, visualizations of the data, and models fit to the data (rtrees and logistic regressions)
- [02-understanding_lime](journals/02-understanding_lime): work done to understand the LIME algorithm
- [03-applying_lime](journals/03-applying_lime)***: applications of LIME to the models fit to the Hamby data
- [04-assessing_lime](journals/04-assessing_lime)***: visual diagnostics for assessing the lime explanations
- [05-iris_comparison](journals/05-iris_comparison): applying LIME to a random forest fit to the iris data and assessing the explanations
- [06-literature_review](journals/06-literature_review/): notes on papers relating to LIME
- [07-computation_issues](journals/07-computation_issues/): documentation of some of the computation issues I ran into during the project
- [08-logistic_regression](journals/08-logistic_regression): examples of applying and diagnosing LIME with logistic regression models fit to the sine data
- [09-identifying_rtrees_training_data](journals/09-identifying_rtrees_training_data/): examples where I retrain the rtrees model with the "current" version of the training data and compare the results
- [10-lime_hamby_variability](journals/10-lime_hamby_variability/): investigating variability between LIME explanations using diagnostic figures for random forest models trained on the Hamby bullet data

*** **Note: We have realized that the training dataset for the `rtrees` model is not the one used in this file. See: [09-identifying_rtrees_training_data](journals/09-identifying_rtrees_training_data)**

[**old-journals**](old-journals)

Contain materials from my earliest research journals relating to the LIME project. It is likely that the code in these files will not run. However, the knit versions of the R markdown documents may still be useful.

@@

- [.gitignore](.gitignore): files to ignore
- [notes from Heike.pdf](notes from Heike.pdf): scans of notes written by Heike for this project
- [README.md](README.md) and [README.Rmd](README.Rmd): this README and the R markdown document used to generate this README
